%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Senior Product Developer} % Job title
    {Synology} % Organization
    {New Taipei City, Taiwan} % Location
    {Jan. 2020 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed a secure login and access flow between Synology Hybrid Share client and Synology C2 Cloud service.}
        \item {Designed and implemented an overall service architecture and event pipelines of Synology Hybrid Share client that supports event dependency with flexibility and efficiency in C++.}
        \item {Built fully automated CI pipelines for Synology Hybrid Share client using Synology automated testing framework to ensure the robustness of the software.}
        \item {Designed and implemented public SDK of Synology Hybrid Share client to integrate Synology software products.}
        \item {Designed and implemented storage throttle policy to reach the goal of uninterrupted file transmission in Synology Hybrid Share client.}
        \item {Designed and implemented data and metadata encryption schemes in Synology Hybrid Share to ensure nearly zero knowledge on the server-side which can protect the privacy of the user.}
        \item {Performance tuning in latency and throughput in Synology Hybrid Share.}
        \item {Be a mentor to help new members finish their tasks and pick up necessary knowledge.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Product Developer} % Job title
    {Synology} % Organization
    {New Taipei City, Taiwan} % Location
    {Sep. 2016 - Jan. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and implemented Synology Virtual DSM license system.}
        \item {Modify Synology Demo Site Service to integrated Synology Virtual DSM.}
        \item {Designed and implemented Virtual Machine Manager public API.}
        \item {Improved the performance of importing/exporting VM in Synology Virtual Machine Manager by modifying QEMU. We save 48\% time in importing and 38\% time in exporting. It also reduces the extra space requirement.}
        \item {Improved the performance of the Synology automated testing framework by about 9\% without modifying CI testing code by letting it be able to run TestSuite parallelly.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer Intern} % Job title
    {Potentia} % Organization
    {Taipei City, Taiwan} % Location
    {April. 2016 - July. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {We built a simple chat bot by using Hubot. I'm responsible for surveying and constructing a Hubot environment which can be simply deployed.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer Summer Intern} % Job title
    {ITRI} % Organization
    {Hsinchu City, Taiwan} % Location
    {July. 2015 - Aug. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {We built a simple song recommender system. I'm responsible for measuring the distance between each songs in this project.}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
